wind_diagrams

### 2019-08-02 wind_analyses.Rmd
Wind_rose (Progress)

wind_match <- match_func(df = wind_daily)

@@

              paddle=FALSE, type="station", width=2))
)
# png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose

# insitu_wind_2 <- insitu_wind %>% 
#   filter(site == "Port Nolloth")
# 
# insitu_wind_3 <- insitu_wind %>% 
#   filter(site == "Lamberts Bay")
# 
# plotPN <- plot(as.factor(format(insitu_wind_2$date, "%Y-%m")), insitu_wind_2$insitu_temp, col = "lightpink")
# plotLB <- plot(as.factor(format(insitu_wind_3$date, "%Y-%m")), insitu_wind_3$insitu_temp, col = "lightpink")
#        
# ?plot
```

>>>>

wind_match <- match_func(df = wind_daily) 
# save(wind_match, file = "Data/wind_match.RData")

@@

              paddle=FALSE, type="station", width=2))
)
# png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose
# ?plot
```

## Wind rose plots

```{r}
# Loading in the matched wind data
load("Data/wind_match.RData")

wind_match <- wind_match %>% 
  drop_na()

wave_daily_renamed <- wind_match %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) 
source("Functions/wind.rose.R")
p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3  # Change colours and remove the NA values
```
